### 2019-04-02 5_evaluation.tex
Small tweaks and edits.
rename parsec dtd shard to parsec shard

Implicitly parallel systems such as PaRSEC, StarPU and Regent that
rely on runtime analysis to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes and thus limits scalability. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs partially, mitigate the
load imbalance in the tasks. Therefore, systems which provide an
additional on-node work stealing capability see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. This can be seen in the difference between Chapel
Distrib (which uses a work stealing scheduler) vs Chapel with its
default (non-work-stealing) scheduler.

>>>>

Implicitly parallel systems such as PaRSEC, StarPU and Regent that
rely on runtime analysis to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes and thus limits scalability. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC Shard.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs only partially mitigates the
load imbalance between tasks. Therefore, systems which provide an
additional on-node work stealing capability see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. This can be seen in the difference between Chapel
Distrib (which uses a work stealing scheduler) vs Chapel with its
default (non-work-stealing) scheduler.
